### 2021-04-03 Chapter-3/Chapter-3.tex
Updates from Overleaf

\subsection{Interpret Instructions Symbolically}
Existing binary analysis \cready{tools}{frameworks}~\cite{shoshitaishvili2016state,
10.1007/978-3-642-22110-1_37, song2008bitblaze} translate machine instructions into
intermediate languages (IR) to simplify analysis since
the variety of machine instructions is
enormous, and their semantics is complex. The Intel Developer
Manual~\cite{intelsys} documents more than 1000 different x86 instructions. 
Unfortunately, the IR layer, which
reduces the workload of these tools, is not suitable for side-channels 
analysis because
IR-based or source code side-channels analyses do not represent the executed instructions accurate enough to analyze fully their control and memory accesses.
For example, a compiler may use conditional moves or bitwise operations to eliminate
branches. Also, as some IRs are not a superset or a subset of ISA, 
it is hard to rule out conditional jumps introduced by IR and add real branches 
eliminated by IR transformations.

@@

\section{Evaluation}

>>>>

\subsection{Interpret Instructions Symbolically}
Existing binary analysis frameworks~\cite{shoshitaishvili2016state,
10.1007/978-3-642-22110-1_37, song2008bitblaze} translate machine instructions into
intermediate languages (IR) to simplify analysis since
the variety of machine instructions is
enormous, and their semantics is complex. The Intel Developer
Manual~\cite{intelsys} documents more than 1000 different x86 instructions. 
Unfortunately, the IR layer, which
reduces the workload of these tools, is not suitable for side-channels 
analysis because
IR-based or source code side-channels analyses do not represent the executed instructions accurate enough to analyze fully their control and memory accesses.
For example, a compiler may use conditional moves or bitwise operations to eliminate
branches. Also, as some IRs are not a superset or a subset of ISA, 
it is hard to rule out conditional jumps introduced by IR and add real branches 
eliminated by IR transformations.

@@

\section{Evaluation}
We evaluate our method on real-world crypto libraries, which include  OpenSSL, mbedTLS, Libgcrypt and Monocypher\@. OpenSSL is the most commonly used crypto libraries in today's software. mbedTLS\@ (previous known as PolarSSL) is designed to be easy to understand and fit on embedded devices. We also evaluate Monocypher, a new cryptographic library that resists to most side-channel attacks. 
Monocypher is designed to have no secret dependent indices and secret dependent branches. Therefore, Monocypher should be secure under our threat model.

Moreover, for some crypto library, we evaluate more than one versions. After that, we compare the evaluation results with the version history to track developers' patches of those leakages.  
\begin{itemize}
\item OpenSSL: 0.9.7, 1.0.2f, 1.0.2k, 1.1.0f, 1.1.1, 1.1.1g
\item MbedTLS: 2.5, 2.15
\item Libgcrypt: 1.8.5
\item Monocyper: 3.0
\end{itemize}

We mark variables and buffers that store a secret.
For DES and AES, we mark symmetric keys as secrets. 
For RSA, we mark private keys as secrets. For ECDSA, 
we mark nonces and private keys as secrets.

\subsection{Evaluation Result Overview}
